¥section{Results}
¥label{sec:results}

Table ¥ref{tab:single_agent_benchmark} reports the results on the single agent scenario comparing the ¥textbf{net score} of BFS planning with PDDL using $A^*$ to find the shortest path to reach a tile.

¥begin{table}[h]
¥centering
¥setlength{¥tabcolsep}{12pt} % Aumenta lo spazio orizzontale tra le colonne
¥caption{Single-agent performance BFS vs PDDL with average net scores.}
¥label{tab:single_agent_benchmark}
¥begin{tabular}{lrr}
¥hline
¥textbf{Map} & ¥textbf{BFS} & ¥textbf{PDDL} ¥¥ ¥hline
26c1¥_1 & 1416 & 1310 ¥¥
26c1¥_2 & 1630 & 1582 ¥¥
26c1¥_3 & 894  & 959  ¥¥
26c1¥_4 & 1463 & 1443 ¥¥
26c1¥_5 & 681  & 782  ¥¥
26c1¥_6 & 2063 & 2364 ¥¥
26c1¥_7 & 1766 & 1794 ¥¥
26c1¥_8 & 1949 & 2044 ¥¥ ¥hline
¥textbf{Average} & ¥textbf{1482.75} & ¥textbf{1534.75} ¥¥ ¥hline
¥end{tabular}
¥end{table}

The performance variations depend strictly on the structural characteristics of each map. BFS achieves higher net scores on maps that are less constrained and well-connected, where sub-millisecond execution allows the agent to react instantly to fast environmental updates. Conversely, on more complex maps (e.g., ¥texttt{26c1¥_3} and ¥texttt{26c1¥_5} through ¥texttt{26c1¥_8}), the strategic value of optimal action sequences computed by the PDDL planner successfully offsets its call overhead. This structural advantage is reflected in the overall performance, with the PDDL pipeline achieving a higher average net score of $1534.75$ compared to the $1482.75$ baseline.



Table‾¥ref{tab:multi_agent_benchmark} reports the scores for the multi-agent scenario, where Agent‾1 is the pure BDI agent and Agent‾2 is the LLM-powered agent.

¥begin{table}[h]
¥centering
¥setlength{¥tabcolsep}{10pt}
¥caption{Multi-agent performance: BDI and LLM-powered agent scores.}
¥label{tab:multi_agent_benchmark}
¥begin{tabular}{lrrc}
¥hline
¥textbf{Map} & ¥textbf{BDI} & ¥textbf{LLM-powered} & ¥textbf{Tested} ¥¥ ¥hline
26c1¥_1 & 1069 & 1262 & $¥checkmark$ ¥¥
26c1¥_2 & 1098 & 1031 & $¥checkmark$ ¥¥
26c1¥_3 & 614 & 614 & $¥checkmark$ ¥¥
26c1¥_4 & 529 & 817 & $¥checkmark$ ¥¥
26c1¥_5 & 401 & 530 & $¥checkmark$ ¥¥
26c1¥_6 & 1697 & 1041 & $¥checkmark$ ¥¥
26c1¥_7 & 1136 & 680 & $¥checkmark$ ¥¥
26c1¥_8 & 1532 & 1687 & $¥checkmark$ ¥¥ ¥hline
¥end{tabular}
¥end{table}

Both agents share the same underlying BDI architecture described in Section‾¥ref{sec:arch}; the LLM layer acts as an additional reasoning module on top of the reactive loop rather than a replacement. 
The score differences across maps are primarily driven by the complexity of the natural language instructions provided to the agents: simpler prompts allow the BDI planner to operate with minimal LLM overhead, while more complex directives introduce latency and occasional misclassifications that reduce the effective score. The results, or points, of the prompts tested are not included on the score, as the current server infrastructure can't take them into account by rendering the admin's inputs and, even if it was the case, they wouldn't produce a fair comparison with the pure BDI's points in ¥ref{tab:single_agent_benchmark}, as it doesn't present an additional source of points.

¥subsection{LLM Components Evaluation Results}
¥label{sec:llm_results}
Table‾¥ref{tab:llm_pipeline_eval} reports a component-level evaluation of the LLM pipeline, measuring the accuracy and average latency of each processing stage across all 315 test cases. Given the focus on architectural validation, the metrics were collected on a controlled test set designed to cover the full range of prompt complexity for each category. While the high overall accuracy (98.4¥%) demonstrates the effectiveness of the targeted few-shot prompts, these figures serve primarily to contextualize execution latency and structural robustness rather than to claim absolute generalization over larger, unconstrained datasets.

¥begin{table}[H]
  ¥centering
  ¥caption{Component-level evaluation of the LLM pipeline (315 total test cases).}
  ¥label{tab:llm_pipeline_eval}
  ¥begin{tabular}{lrrrr}
    ¥toprule
    ¥textbf{Category} & ¥textbf{Total} & ¥textbf{Passed} & ¥textbf{Avg.¥ latency (ms)} ¥¥
    ¥midrule
    ¥texttt{tools}                    & 50 & 50 &   2 ¥¥
    ¥texttt{splitMessage}             & 35 & 34 & 764 ¥¥
    ¥texttt{extractCityName}          & 25 & 25 & 282 ¥¥
    ¥texttt{extractMathExpression}    & 25 & 24 & 372 ¥¥
    ¥texttt{extractDeliveryConstraint}& 25 & 25 & 667 ¥¥
    ¥texttt{decideNextAction}         & 25 & 25 & 323 ¥¥
    ¥texttt{generateDesire}             & 23 & 23 & 1401 ¥¥
    ¥texttt{extractStackConstraint}     &  8 &  8 & 1549 ¥¥
    ¥texttt{extractMultiAgentCommand}   & 22 & 22 &  509 ¥¥
    ¥texttt{decideNextAction}           & 44 & 44 &  203 ¥¥
    ¥midrule
    ¥textbf{Total}                      & ¥textbf{282} & ¥textbf{280} & --- ¥¥
    ¥bottomrule
  ¥end{tabular}
¥end{table}