\section{Conclusion}
\label{sec:conclusion}

This work presented a full-stack autonomous agent for the Deliveroo.js environment, combining a deliberative BDI loop, a PDDL-based path planner, an LLM natural-language interface, and a cooperative multi-agent protocol.

In the single-agent scenario, the PDDL planner achieved a higher average net score ($1534.75$) than the BFS baseline ($1482.75$), confirming that the overhead of optimal path computation is outweighed by the quality of the resulting plans on structurally complex maps. The BDI loop provided a reliable reactive backbone, with the PDDL layer adding strategic depth where it was most needed.

In the multi-agent scenario the picture is more nuanced. The LLM-powered agent outperforms its pure-BDI counterpart on several maps (e.g., \texttt{26c1\_1}, \texttt{26c1\_4}, \texttt{26c1\_5}, \texttt{26c1\_8}), demonstrating that natural-language reasoning can translate into actionable decisions that improve parcel collection. However, on maps with faster parcel turnover (e.g., \texttt{26c1\_6}, \texttt{26c1\_7}) the cumulative latency of the LLM pipeline erodes this advantage, and the reactive BDI agent scores considerably higher. This trade-off is consistent with the pipeline evaluation, where individual LLM calls range from 2\,ms to over 1.5\,s depending on task complexity, and with the 98.4\% overall accuracy indicating that errors, while rare, do occur under complex prompts.

Taken together, the results confirm that combining symbolic reasoning with natural-language understanding produces a more versatile agent, capable of handling instructions that a purely reactive system could not interpret. The main trade-off is speed: the richer the reasoning, the more time it takes, and fast-paced environments tend to reward quick reactions over deliberation. Closing this gap remains an open direction for future work.
